---
title: "Adidas_sales"
author: "Joshua"
date: "2023-06-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Adidas Sales store

Adidas AG (German: [ˈʔadiˌdas] ( listen); stylized as adidas since 1949) is a German athletic apparel and footwear corporation headquartered in Herzogenaurach, Bavaria, Germany. It is the largest sportswear manufacturer in Europe, and the second largest in the world, after Nike. 

Adidas AG, the adidas group, is one of the largest manufacturers of sports shoes and clothing in Europe and the second-biggest in the world after the main competitor Nike. Adidas produces and sells sports clothing, sneakers, running shoes, bags, accessories like watches and sunglasses, and so on through its e-com shop, over a thousand retail stores, and several franchises. The brand is headquartered in Herzogenaurach, Germany.

Were going to focus on the USA Sales in this analysis
THE DATASET was download from github account 


```{r adidas}
# load the packages

library(tidyverse)
library(readr)
library(dplyr)
library(ggplot2)
library(janitor)
library(readxl)

```

```{r}
df <- read_xlsx("Adidas Sales (2020-2021).xlsx")
```


Data Wrangling and cleaning

```{r}
head(df)
```

```{r}
summary(df)
```
```{r}
summary(df$`Price per Unit`)

```




```{r}
#count the  null value
sum(is.na(df))
unique(count(df))
```


```{r}
# 
sum(duplicated(df))
```
```{r}
#cleaning the column
adidas <- df %>%  clean_names()
```

```{r}
str(adidas)
```
 **Now we can analyze the data**
```{r}
plot(adidas$price_per_unit)
```
```{r}

ggplot(adidas, aes(x=price_per_unit, y=units_sold )) + 
  geom_point(aes(color=sales_method )) + 
  labs(y="unite", 
       x="price", 
       title="price per unit and unite sold vs sold methode ")+ 
       theme_gray()+ # Default theme 
        theme(plot.title = element_text(size=22),axis.text.x= element_text(size=15),
                            axis.text.y= element_text(size=15), axis.title=element_text(size=18))
```




```{r}
ggplot(adidas, aes( x =retailer,  y= total_sales)) + 
  geom_col(aes(fill=retailer )) + 
  labs(x=" ", 
       y="amount",
       title="Quality of Education Vs Score against Country & Citations")+ 
        theme_bw()+
theme(plot.title = element_text(size=22),axis.text.x= element_text(size=15,angle=90),
                            axis.text.y= element_text(size=15), axis.title=element_text(size=18))
```





```{r}
ggplot(adidas, aes(x=units_sold ,y=total_sales, color=region)) +
  geom_jitter(width = .5, size=2)+  # Adjusting size and width of points
    labs(x="unit",
         y="total sold", 
       title="total sales vs unit_sold ")+ 
theme_bw()+
theme(plot.title = element_text(size=22),axis.text.x= element_text(size=15),
                            axis.text.y= element_text(size=15), axis.title=element_text(size=18))
```
```{r}
ggplot(adidas, aes(x= region, y=total_sales, fill=sales_method))+
geom_col(position='dodge', width = 0.5)+  # Stack for stacked chart
 labs(x=" ",
         y="Count", 
       title="Distribution of sales per region")+ 
theme_bw()+
theme(plot.title = element_text(size=22),axis.text.x= element_text(size=15,angle=90),
                            axis.text.y= element_text(size=15), axis.title=element_text(size=18))
```
```{r}
ggplot(adidas, aes(x= product, y=total_sales, fill=sales_method))+
geom_col(position='dodge', width = 0.5)+  # Stack for stacked chart
 labs(x=" ",
         y="Count", 
       title="Distribution of sales per region")+ facet_wrap(~region) +
theme_bw()+
theme(plot.title = element_text(size=12),axis.text.x= element_text(size=12,angle=90),
                            axis.text.y= element_text(size=12), axis.title=element_text(size=13))
```
```{r}
ggplot(adidas, aes(x= product, y=total_sales, fill=region))+
geom_col(position='dodge', width = 0.7)+  # Stack for stacked chart
 labs(x=" ",
         y="Count", 
       title="Distribution of sales per region")+ 
theme_bw()+
theme(plot.title = element_text(size=22),axis.text.x= element_text(size=15,angle=90),
                            axis.text.y= element_text(size=15), axis.title=element_text(size=18))
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```


